### 2024-04-10 doc/sections/introduction.tex
Draft version for MFPS 2024
[ tex ] cite journal version of BV/POMset logic complexity

We present an algebraic semantics and semantic proof of generalised cut-elimination for the multiplicative-additive system MAV~\cite{Horne15:mav}, which extends the basic system BV\footnote{
      BV stands for \underline{B}asic System \underline{V}irtual, owing to an early interpretation of CCS interaction as the pairwise production and annihilation of virtual particles in physics~\cite[\Fn2]{Horne15:mav}.
}~\cite{Guglielmi99:bv,Guglielmi07:sis} with the additives of multiplicative-additive linear logic~\cite[MALL]{Girard87:ll}. The proof technique also extends to the additive units.
Our proofs are constructive and mechanised in Agda~\cite{Agda264}.

@@

MAV and BV are \emph{Deep Inference} systems. Deep Inference~\cite{Guglielmi14:di} is generalisation of Gentzen's methodology for designing proof systems, which arose from Guglielmi's attempts to relate process algebra~\cite[CCS]{Milner80:CCS,Milner89:CC} to Classical Linear Logic~\cite[CLL]{Girard87:ll}.
The problem with such a relation is that, while the multiplicative connectives of Linear Logic capture parallel composition, no connective of Linear Logic captures \emph{sequential composition}.
Eventually, Guglielmi's attempts yielded BV, which extends Multiplicative Linear Logic~\cite[MLL]{Girard87:ll} with a self-dual non-commutative connective that captures sequential composition.
Such a connective was already present in another extension of Linear Logic, Pomset logic~\cite{Retore97:pomset}, where it arose from the study of coherence space semantics of Linear Logic~\cite[\C8]{GirardTL89:proofs}.
Recently, Nguyễn and Stra{\ss}burger~\cite{NguyenS22:bvisnotpl} showed that, while BV is similar to Pomset logic, the two are not the same, as the theorems of BV form a proper subset of the theorems of Pomset logic.
Neither BV nor Pomset logic has a sequent calculus. Tiu~\cite{Tiu06:sisii} showed that sequent calculus cannot capture BV, and it is assumed that this result extends to Pomset logic.

>>>>

We present an algebraic semantics and semantic proof of generalised cut-elimination for the multiplicative-additive system MAV~\cite{Horne15:mav}, which extends the basic system BV\footnote{
      BV stands for \underline{B}asic System \underline{V}irtual, owing to an early interpretation of CCS interaction as the pairwise production and annihilation of virtual particles in physics~\cite[\Fn2]{Horne15:mav}.
}~\cite{Guglielmi99:bv,Guglielmi07:sis} with the additives of multiplicative-additive linear logic~\cite[MALL]{Girard87:ll}. The proof technique also extends to the additive units and the exponentials.
Our proofs are constructive and mechanised in Agda~\cite{Agda264}.

@@

MAV and BV are \emph{Deep Inference} systems. Deep Inference~\cite{Guglielmi14:di} is generalisation of Gentzen's methodology for designing proof systems, which arose from Guglielmi's attempts to relate process algebra~\cite[CCS]{Milner80:CCS,Milner89:CC} to Classical Linear Logic~\cite[CLL]{Girard87:ll}.
The problem with such a relation is that, while the multiplicative connectives of Linear Logic capture parallel composition, no connective of Linear Logic captures \emph{sequential composition}.
Eventually, Guglielmi's attempts yielded BV, which extends Multiplicative Linear Logic~\cite[MLL]{Girard87:ll} with a self-dual non-commutative connective that captures sequential composition.
Such a connective was already present in another extension of Linear Logic, Pomset logic~\cite{Retore97:pomset}, where it arose from the study of coherence space semantics of Linear Logic~\cite[\C8]{GirardTL89:proofs}.
Recently, Nguyễn and Stra{\ss}burger~\cite{NguyenS22:bvisnotpl,NguyenS23:complexity} showed that, while BV is similar to Pomset logic, the two are not the same, as the theorems of BV form a proper subset of the theorems of Pomset logic.
Neither BV nor Pomset logic has a sequent calculus. Tiu~\cite{Tiu06:sisii} showed that sequent calculus cannot capture BV, and it is assumed that this result extends to Pomset logic.
